### 2018-09-27 FrascatiPlot/Paper/aps/main.tex
Axe keeps falling...

\section{Introduction} 
The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions.
Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, kaons, protons, etc.), because their size is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.  
The relevant known properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave-function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. 
For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange nuclei with mass number $A = 3$, driven by the average separation of the $\Lambda$ with respect to the two other nucleons.

@@

For about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
Surprisingly, thermal-statistical models have been successful in describing also the production of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2010qu,Andronic:2017}. 
In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}. Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease. Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances. Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically at temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}. 
In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects. For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}. 
Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.   
Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}. 
Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of the coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}. 
Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.

To this purpose, we compare to models the existing data from the LHC. For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size. 
In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities.

A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with the hyper-nuclei proposed here.
Based on our findings, we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample foreseen at the LHC Run 3 \& 4, in order to discriminate the aforementioned scenarios.

@@

In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}. 
For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$.
Considering that at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as

\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
%
The LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. As a consequence, the anti-particle to particle ratio for (hyper-)nuclei is measured to be consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

More advanced coalescence models take into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
As coalescence is a quantum-mechanical process, the classical definition of phase space is replaced by the Wigner formalism. Therefore, the production probability of a nucleon cluster is given by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.
The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with one single characteristic-size parameter, $r_{A}$. 
For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains

@@

\noindent For nuclei with $A > 2$, analogous forms exist. The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as

@@

\noindent for point-like constituents. In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$.
In this work, we follow the gaussian ansatz in order to obtain fully analytic solutions that highlight the sensitivity to the size of the source (i.e. the centrality dependence) and to the size of the (hyper-)nucleus. 
In Tab.~\ref{tab:nucleusradii}, we list the measured rms of the wave-function, $\rmsradius^{meas}$, as well as the $r_{A}$ parameter derived according to these relations. 
We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with more realistic wave-functions, e.g. the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.

The quantum-mechanical nature of the coalescence products is explicitly accounted for by means of an average correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum-mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. The coalescence parameter decreases with increasing volume, as expected. 
The quantum-mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to

\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm~\cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.~\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm. The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the vertical dotted line for $\dradius = 3.2$ fm.}}
\label{fig:radiusDependence}
\end{center}
\end{figure}

Following the approach and discussion presented in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as

\begin{equation}
\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
\label{eq:CA_general}
\end{equation}
%
for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 in~\cite{Scheibl:1998tk}.
In particular, for the case of \hethree~with $A=3$ and $J=1/2$, the latter becomes the Eq. 9 presented in~\cite{Blum:2017qnn}.

In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq. 6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:

\begin{equation}
	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;\; .
\end{equation}

\noindent This formula can be used to compare the predicted $B_{A}$ with experimental data directly.

 We understand the relation between $B_A$ and the radii as follows: for small radii of the source, as $R \rightarrow 0$, the coalescence probability appears to be anti-proportional to the harmonic oscillator size parameter $r_A$, and thus proportional to the depth of the attractive potential in the harmonic oscillator picture (and thus to the nucleus binding energy).
Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
For a large source volume, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, and thus decreases for large distances in configuration space.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=.8\columnwidth]{../HbtRadiusParam.png}
\caption{Parameterisation A of the dependence of the source radius on multiplicity compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}. The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
\label{fig:radiiparam}
\end{center}
\end{figure}

@@

%\begin{figure*}[htbp]
%	\begin{center}
%		\includegraphics[width=\textwidth]{../radiiParamCompareData.png}
%		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions. The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
%		\label{fig:CompareB2B3forDifferentParamWithData}
%	\end{center}
%\end{figure*}

>>>>

\section{Introduction} 
Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, protons, etc.), because their size is comparable to a fraction or the whole system created in high-energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions~\cite{Adam:2015vna}.  
Their size is typically defined as the rms of their (charge) wave-function, corresponding to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. 
For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ with respect to the two other nucleons.
The properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.

@@

For about sixty years, coalescence models have been used to describe the formation of composite objects \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf}.
Surprisingly, thermal-statistical models have been successful in describing also the production of light (anti-)(hyper-)nuclei across a wide range of energies in AA collisions \cite{Andronic:2010qu,Andronic:2017}. 
In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV.
Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease. Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances. Once the mean free path for elastic collisions is larger than the system size, the fireball freezes-out kinetically at $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}. 
In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile''. 
For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
The cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}. 
Similarly, the elastic cross-section driving deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.   
The deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase, yet their production is measured to be consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc}. 
Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}. 
Data from rescattering of short-lived hadronic resonances suggest a long-lasting hadronic phase \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in this letter.

To this purpose, we compare LHC data to models. 
For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system- and object-size. 
A quantitative comparison of the two scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the comparison with the hyper-nuclei proposed here.
We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample foreseen at the LHC Run 3 \& 4, in order to discriminate the aforementioned scenarios.

@@

In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}. 
For a nucleus with mass number $A = Z + N$, the coalescence probability is quantified by the coalescence parameter $B_{A}$.
Considering that at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as

\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
%
The LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. Consequently, the anti-particle to particle ratio for (hyper-)nuclei is consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.

In a simple coalescence approach, \bA~is expected to be independent of momentum and of the object size relative to the volume of particle emission (hereafter referred to as ``source volume'' or ``size'').
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}. 
The elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

More advanced coalescence models \cite{Sato:1981ez, Nagle:1996vp, Scheibl:1998tk} take into account the source size, as the coalescence probability naturally decreases for nucleons with similar momenta that are produced far apart in configuration space. We rely on the formalism proposed in~\cite{Scheibl:1998tk}.
As coalescence is a quantum-mechanical process, the classical definition of phase space is replaced by the Wigner formalism. The production probability of a nucleon cluster is given by the overlap of the Wigner function with the phase-space distributions of the constituents.
The wave-functions of the (hyper-)nuclei are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with one single characteristic-size parameter, $r_{A}$. 
For the deuteron wave-function $\varphi_{d}(\vec{r}) $, one obtains

@@

\noindent For nuclei with $A > 2$, analogous forms exist. The relation between $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as

@@

\noindent for point-like constituents. 
We follow the gaussian ansatz to obtain fully analytic solutions.
In Tab.~\ref{tab:nucleusradii}, we list the measured rms of the wave-function, $\rmsradius^{meas}$, and the $r_{A}$ parameter derived from these relations. 
We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with more realistic wave-functions, e.g. the Hulthen parameterisation for deuterons \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for hyper-tritons as done only for central collisions in~\cite{Zhang:2018euf}.

The quantum-mechanical nature of the coalescence products is explicitly accounted for by means of an average correction factor, $\langle C_{A} \rangle$. For deuterons, $\langle C_{d} \rangle$ has been approximated as

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the size parameter, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The nucleus size enters in the  calculation of \btwo~via $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation~\cite{Scheibl:1998tk}
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})} \;\; .
\label{eq:B2cd}
\end{equation}
%
The coalescence parameter decreases with increasing volume, as expected. 
$\langle C_{d} \rangle$ introduces a length scale defined by the deuteron size relative to the source size. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to

\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%

Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of $\langle C_{d} \rangle$ and \btwo, calculated assuming (a.) $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value $\dradius = 3.2$ fm~\cite{Mohr:2015ccw}, (d.) a larger, irrealistic $\dradius = 10$ fm. 
As shown in Fig. \ref{fig:radiusDependence}, $\langle C_{d} \rangle$ suppresses significantly the production of objects with radius larger than the source.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=.8\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.~\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm. The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the vertical dotted line for $\dradius = 3.2$ fm.}}
\label{fig:radiusDependence}
\end{center}
\end{figure}

Following the discussion in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as

\begin{equation}
\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)} \;\; .
\label{eq:CA_general}
\end{equation}
%
Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 of~\cite{Scheibl:1998tk}.
For the case of \hethree, the latter becomes Eq. 9 of~\cite{Blum:2017qnn}.

In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see next section) and by combining Eq. 6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain:

\begin{equation}
	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;.
\end{equation}

\noindent This general formula can be used to compare the predicted $B_{A}$ with data directly.

For small sources, as $R \rightarrow 0$, the coalescence probability is anti-proportional to the harmonic oscillator size parameter, and thus proportional to the depth of the attractive potential in the harmonic oscillator picture (and thus to the nucleus binding energy).
Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
For a large source, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, thus decreases for large distances in configuration space.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\columnwidth]{../HbtRadiusParam.png}
\caption{Parameterisation A of the dependence of the source radius on multiplicity compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}. The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
\label{fig:radiiparam}
\end{center}
\end{figure}

@@

### 2018-09-27 FrascatiPlot/Paper/aps/table1.tex
Axe keeps falling...

\begin{ruledtabular}
\begin{tabular}{cccccccc}\\[-2ex]
Mass number & Nucleus &  Composition  & $B_{E}$ (MeV)   &  $J_{A}$ & \rmsradius$^{meas}$~(fm) &  $r_{A}$ (fm) & Refs. 
\\[0.5ex] \hline \\[-2ex]
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
      A = 3  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
                                   A = 4  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1    &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]

\end{tabular}
\end{ruledtabular}

\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$. $B_{E}$ is the binding energy in MeV, $J_{A}$ is the spin. The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
 %References are given in the last column.}
%. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.
\label{tab:nucleusradii}
\end{table*}

>>>>

\begin{ruledtabular}
\begin{tabular}{cccccccc}\\[-2ex]
Mass number & Nucleus &  Composition  & $B_{E}$ (MeV)   &  $J_{A}$ & \rmsradius$^{meas}$~(fm) &  $r_{A}$ (fm) & Refs. 
\\[0.5ex] \hline \\[-2ex]
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
      A = 3  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]                                    
\end{tabular}
\end{ruledtabular}

\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 3$. $B_{E}$ is the binding energy in MeV, $J_{A}$ is the spin. The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
 %References are given in the last column.}
%. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.
\label{tab:nucleusradii}
\end{table*}
